I am a passionate programmer who has been writing code for over ten years. I work with back-end web development at Cantemo, and I wrote my master's thesis in the area of video compression.

I am a self-starter who likes personal responsibility and I take pride in writing clear and effective code. I know how to work independently -- how to use Google to my advantage -- and how to function as a member of a team, never afraid to ask for help and always happy to help others. I am a social person who thrives in the company of others, I love to travel and would like to pursue an international career at some point in the future.

I enjoy using a multitude of programming languages. Python is my go-to language for any high-level task. I just love how flexible it is and that the syntax reads like plain English. Django and Flask are also great tools for web development. I use JavaScript often in my current position, developing in React, Backbone, jQuery together with HTML and CSS. I have also written a few Chrome extensions with "vanilla" JavaScript.

C\texttt{++} and Java are great companions because of the wealth of available libraries, and I have experience with low-level C. Writing malloc/free from scratch, implementing my own shell and performing video bitstream manipulation. I am always eager to pick up new technologies and I know my way around the basics of Ruby and Perl.

I have been a Unix user for many years, starting with Ubuntu in 2008 and now primarily Mac OS X. I love using the terminal and will often spend my spare time writing shell scripts for all kinds of tasks; extracting segments from a media file using ffmpeg, splitting or merging git repositories, or just playing around with config files.

I was always a high-achieving student with a big interest in mathematics. I tailored my university education to be able to write as much code as possible and took courses in functional languages, assembler, real-time programming/concurrency, natural language processing (NLP), computer security and advanced algorithm theory -- as well as all the basics of recursion, complexity, graph theory and discrete mathematics.

I have contributed to a number of open source projects like Oh My Zsh, Last.fm Scrobbler, qBittorrent and Qt. I wrote my own web scraper to collect and compare odds data from betting sites in order to find arbitrages (sure bets). I created a tool for scraping tracklists and cover art from Bandcamp and Spotify's API and simulated browser actions with Selenium to automatically navigate Rateyourmusic.com to add the information there. I also have some experience creating 2D platformer games using the Pygame library which was a lot of fun.

Thanks for your time, I look forward to hearing back from you soon!
